---
title: "final-report"
author: "Rashaad Ratliff-Brown"
date: "12/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
library(tidyverse)
library(readxl)
library(tidyr)
```


```{r}
#load data
data <- read.csv("stockx.csv")
data$Release.Date <- as.Date(as.character(data$Release.Date), format="%m/%d/%y")
data$Order.Date <- as.Date(as.character(data$Order.Date), format="%m/%d/%y")
data$Since.Release <- difftime(data$Order.Date,data$Release.Date, units = "days")
data$Difference <- data$Sale.Price - data$Retail.Price
data$Shoe.Size <- factor(data$Shoe.Size)
data$Buyer.Region <- factor(data$Buyer.Region)
data$Type <- factor(data$Type)
data$Colorway <- factor(data$Colorway)
data
```

**Summary: **

Inferential questions evaluted in this analysis all surround the factors that impact the resale (after retail) value of a sneaker. Multiple Linear Regression was used to evalute a retrieved dataset to seek insight, support, and answers to our inferential questions. During the process of the analysis it was clear that sneaker style and colorway had a statistically significant impact on the  

**Introduction: **

**Data: **

**Model: **

**Conclusion: **

**Appendix **